Peer Assessment 1 - Reproducible Research
========================================================

# Reproducible Research: Peer Assessment 1

## Loading and preprocessing the data
```{r readData}
library(ggplot2)

temp = tempfile()
download.file("http://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip", temp)
pdata = read.csv(unz(temp, "activity.csv"), colClasses = c("numeric", "Date", "numeric"))

```


## What is mean total number of steps taken per day?
```{r steps_per_day, fig.width=6, fig.he0ight=6}

steps_day <- aggregate(steps ~ date, pdata, sum)  
ggplot(steps_day, aes(x=steps)) + geom_histogram()


day_ave = mean(steps_day[,2])
day_median = median(steps_day[,2])
```


## What is the average daily activity pattern?
```{r interval,  fig.width=6, fig.he0ight=6}
steps_interval <- aggregate(steps ~ interval, pdata, mean)
plot(steps_interval[,1],steps_interval[,2], type = "l")

interval_max = max(steps_interval[,2])

```


## Imputing missing values
```{r filling}
# Number of missing values
miss_rows = is.na(pdata$steps)
tot_miss_rows = dim(pdata)[1] - table(miss_rows)[1]

# Filling in values
interval_mean = rep(steps_interval[,2],61)

# Create a new dataset
pdata$steps[miss_rows] =  interval_mean[miss_rows]

# Make a histogram of the total number of steps taken each day and Calculate and report the mean and median total number of steps taken per day.
steps_day_2 <- aggregate(steps ~ date, pdata, sum)  

ggplot(steps_day_2, aes(x=steps)) + geom_histogram()


day_ave = mean(steps_day[,2])
daymedian = median(steps_day[,2])

```

The new mean is `r day_ave` and the median is `r day_median` after filling in the incomplete rows. 

## Are there differences in activity patterns between weekdays and weekends?
```{r weekday}

logic_vect= (weekdays(pdata$date) == "Sunday" | weekdays(pdata$date) == "Saturday")
week = factor(logic_vect, labels = c("weekday", "weekend"))

factored_data = cbind(pdata, week)


# Get average of steps per weekend day in a given interval
steps_per_interval <- aggregate(steps ~ interval,factored_data[logic_vect,], mean)


# Get average of steps per weekday in a given interval
steps_per_interval_end <- aggregate(steps ~ interval, factored_data[!logic_vect,], mean)


par( mfcol = c(2,1), mar=c(4,4,2,2), oma = c(0,0,2,0) )

plot(steps_per_interval$interval,steps_per_interval$steps, type = "l" ,xlab = 'Interval',ylab = 'Average steps')
title(main ='Weekend pattern')

plot(steps_per_interval_end$interval, steps_per_interval_end$steps, type = 'l', xlab = 'Interval',ylab = 'Average steps')
title(main ='Weekday pattern')


```



